Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-25 appendix.tex
tex

>>>>

	\item [T] Sam's idea is interesting. By incorporating the idea of
		on-manifold adversarial example to adversarial training, the
		performance on benign example is greatly improved.
		%
		That idea can be interpreted as to be selective on the adversarial
		example used for trianing.
		%
		Here, in our observation, we are also selective on the adversarial
		examples used for training.
		%
		Is there anything in common?

	\item [T] Face recognition methods such as ArcFace can be used for
		metric learning.
		%
		We have an opportunity of smooth transition to defense for face
		recognition methods.
		%
		Is defense for face recognition missing from the literature?
